Comparing ChatGPT-4 to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6939 Deaths in Sierra Leone from 2019-2022

### 2024-02-10 manuscript/manuscript.tex
Working on results text

Of the 6939 records, ChatGPT-4 had the highest PCCC overall and for the adult, child, and neonatal age groups. ChatGPT-3.5 performed better than InterVA-5 and InSilicoVA overall and for the adult and child age groups, but worse than InSilicoVA for the neonatal age group. Figure \ref{fig-perf-agegroup} shows the overall PCCC performance by age group with reference to the CSMF Accuracy.

>>>>

Of the 6939 records, ChatGPT-4 had the best performance overall followed by ChatGPT-3.5, InSilicoVA, and InterVA-5 at 0.71, 0.64, 0.44, and 0.43 PCCC respectively. CSMF Accuracies followed the same pattern except for InterVA-5 and InSilicoVA, where InterVA-5 had a higher CSMF Accuracy at 0.78 compared to InSilicoVA at 0.74. Figure \ref{fig-perf-agegroup} shows the PCCC performance across age groups with reference to the CSMF Accuracy. ChatGPT-4 also had the best performance across all three age groups, while ChatGPT-3.5 and InSilicoVA had similar performance (within 0.05 PCCC) for child and neonatal records respectively. ChatGPT-3.5 did worse than InSilicoVA for neonatal records at 0.51 PCCC whereas it had performances close to ChatGPT-4 for the adult and child age groups.

\begin{table}[h]
\caption{Overall model performance for physician agreed records (n=6939)}\label{tab-perf-overall}%
\begin{tabular}{@{}llll@{}}
\toprule
Model & PCCC (0=Low, 1=High)  & CSMF Accuracy (0=Low, 1=High)\\
\midrule
ChatGPT-4 & 0.71 & 0.89\\
ChatGPT-3.5 & 0.64 & 0.86\\
InSilicoVA & 0.44 & 0.74\\
InterVA-5 & 0.43 & 0.78\\
\botrule
\end{tabular}
\footnotetext{Note: Models sorted from highest to lowest PCCC.}
\end{table}
